### 2023-11-09 Data/AnalysisData/codebook_data_H1.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:46.380662"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H1.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:37.92829"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_h1.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-09 Data/AnalysisData/codebook_data_H2.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:49.767935"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H2.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:42.481222"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_h2.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-09 Data/AnalysisData/codebook_data_H3_avg.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:55.749084"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H3_avg.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:45.103283"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_h3_avg.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-09 Data/AnalysisData/codebook_data_H3_multiple.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:53.662957"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H3_multiple.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:43.923892"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_h3_multiple.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-09 Data/AnalysisData/codebook_data_H4.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:23.774949"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H4.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:31.706902"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_h4.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-09 Data/AnalysisData/codebook_data_H5.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:56:39.032172"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H5.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:36.127949"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_h5.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-09 Data/AnalysisData/codebook_data_H6.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:47:39.749165"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H6.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:34.332851"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_h6.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-09 Scripts/Manuscript/manuscript.Rmd
added the replicability and reliability test table.

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```
```{r Hypothesis 2 Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_h2))

# and same analyses for omega
# intercept only model to check the within and between group variance.
H2_test_result_omega <- summary(lmer(formula = omega.tot ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),]))

@@

```{r ICC calculations, include = FALSE}
# alpha
# within group variance: 0.04384
# between group variance: 0.19824
ICC_alpha <- 0.19824 / (0.04384 + 0.19824)

# omega
# within group variance: 0.003779
# between group variance: 0.034025
ICC_omega <- 0.034025 / (0.003779 + 0.034025)

@@

```{r Hypothesis 3 Main Test, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
                                     family = binomial(), data = data_h3_avg))

# and for omega
H3_test_result_main_omega <- summary(glm(formula = replication ~ 1 + 
                                     omega.tot_avg, family = binomial(), 
                                     data = data_h3_avg))

@@

```{r Hypothesis 3 Multilevel Model Sensitivity Analyses, include = FALSE}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h3_multiple))

# and for omega
H3_test_result_int_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
                                                + omega.tot + (1|g), family = 
                                                  binomial(), data = 
                                                  data_h3_multiple))

@@

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

# and for omega
H3_test_result_slp_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
                                                + omega.tot + (1 + omega.tot|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

@@

The average Cronbach's alpha coefficient across replication sets was $0.618$ with a standard deviation of $0.554$, for omega the mean was $0.773$ with a standard deviation of $0.161$. Figure XXX shows the distributions of the Cronbach's alpha coefficients for each replication set separated by successful and unsuccessful replication.

INSERT PLOT 34

The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas XXX, XXX, & XXX. The between-group and within-group variance for Cronbach's alpha were approximately $0.198$ and $0.044$ respectively. The resulting ICC, obtained using formula XXX, was approximately $0.819$. This suggests that variance was larger between replication sets than within. The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance $= 0.034$, within-group variance $= 0.004$, ICC = $0.900$). Both results are in line with hypothesis 2, although caution in interpreting this result is advised due to the small sample size and the lack of an available inferential test.

@@

INSERT REPLICABILITY AND RELIAIBLITY TESTS TABLE HERE

Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: $B = -1.621, SD = 1.527, p = .288$; omega: $B = 0.495, SD = 3.776, p = .896$), nor in any of the multilevel sensitivity analyses models (see Table XXX). This is contradictory to the expectation in hypothesis 3. However, the results from these analyses should be evaluated with caution, given the small sample number of measures used to estimate these models.

@@

>>>>

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)
library(ggplot2)
library(grid)
library(gridExtra)

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```
```{r Hypothesis 2 Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)

# and same analyses for omega
# intercept only model to check the within and between group variance.
H2_test_result_omega <- lmer(formula = omega ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),])

@@

```{r ICC calculations, include = FALSE}
# alpha
within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2

ICC_alpha <- between_group_variance_alpha / (within_group_variance_alpha + between_group_variance_alpha)

# omega
within_group_variance_omega <- attr(VarCorr(H2_test_result_omega), "sc")^2
between_group_variance_omega <- attr(VarCorr(H2_test_result_omega)$g, "stddev")^2

ICC_omega <- between_group_variance_omega / (within_group_variance_omega + between_group_variance_omega)

@@

```{r Hypothesis 3 Main Test, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- apa_print(glm(formula = replication ~ 1 + alpha, 
                                      family = binomial(), data = data_h3_avg))

# and for omega
H3_test_result_main_omega <- apa_print(glm(formula = replication ~ 1 + 
                                     omega, family = binomial(), 
                                     data = data_h3_avg))

@@

```{r Hypothesis 3 Multilevel Model Sensitivity Analyses, include = FALSE}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h3_multiple))

# and for omega
H3_test_result_int_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
                                                + omega + (1|g), family = 
                                                  binomial(), data = 
                                                  data_h3_multiple))

@@

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

# and for omega
H3_test_result_slp_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
                                                + omega + (1 + omega|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

@@

The average Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`, for omega the mean was `r apa_num(sd(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`. Figure XXX shows the distributions of the Cronbach's alpha coefficients for each replication set separated by successful and unsuccessful replication.

```{r Plot 23 Alpha Code}
# plot for alpha
ggplot(plot_23_data_alpha, aes(x = alpha, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 6.5, color = "red", size = 1) +
  geom_point(alpha = 0.1) +
  theme_minimal() +
  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
                                                     "lines")) +
  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
    ymin = 7, ymax = 7, xmin = 1.08, xmax = 1.08) +
  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
  coord_cartesian(xlim = c(0, 1), clip = "off") +
  ylab("") +
  xlab("Cronbach's alpha")

```{r Plot 23 Omega Code, include = FALSE, eval = FALSE}
# plot for omega
ggplot(plot_23_data_omega, aes(x = alpha, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 6.5, color = "red", size = 1) +
  geom_point(alpha = 0.1) +
  theme_minimal() +
  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
                                                     "lines")) +
  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
    ymin = 5, ymax = 5, xmin = 1.08, xmax = 1.08) +
  coord_cartesian(xlim = c(0, 1), clip = "off") +
  ylab("") +
  xlab("Omega")

The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas XXX, XXX, & XXX. The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively. The resulting ICC, obtained using formula XXX, was approximately `r apa_num(ICC_alpha, digits = 3)`. This suggests that variance was larger between replication sets than within. The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance `r apa_num(within_group_variance_omega, digits = 3)`, within-group variance `r apa_num(between_group_variance_omega, digits = 3)`, ICC = `r apa_num(ICC_omega, digits = 3)`). Both results are in line with hypothesis 2, although caution in interpreting this result is advised due to the small sample size and the lack of an available inferential test.

@@

```{r Replicability and Reliability Test Table}
# creating the dtaframe for the table
H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)

# adding an asterix for significance to the significant p in the dataframe
H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "^*")

# adding rows to give indication of specific sections (apa_table being awkward)
H3_table_for_printing <- rbind(c("Alpha", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[1:2,], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(9:10),])

# print the table in apa formatting
apa_table(
  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
  , caption = "Model Results from Tests of Hypothesis 3"
  , note = "The Cronbach's alpha section shows the models where the calculated Cronbach's alpha coefficient was the independent variable. In the Omega section it was the calculated omega coefficient. The random slope model for Cronbach's alpha did not converge, thus it results are not shown here. $^* p < .05$"
  , escape = FALSE, placement= "ht", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))

Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbachs alpha: `r H3_test_result_main_alpha$full_result$alpha`; omega: `r H3_test_result_main_omega$full_result$omega`), nor in any of the multilevel sensitivity analyses models (see Table XXX). This is contradictory to the expectation in hypothesis 3. However, the results from these analyses should be evaluated with caution, given the small sample number of measures used to estimate these models.

@@

```{r}
#apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)
